Quarto Template for Springer Nature

### 2025-03-27 template.tex
First commit

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  sn-basic,
]{sn-jnl}

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\raggedbottom
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\usepackage{amsthm}
\theoremstyle{plain}
\newtheorem{proposition}{Proposition}[section]
\theoremstyle{remark}
\AtBeginDocument{\renewcommand*{\proofname}{Proof}}
\newtheorem*{remark}{Remark}
\newtheorem*{solution}{Solution}
\newtheorem{refremark}{Remark}[section]
\newtheorem{refsolution}{Solution}[section]
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Tail Flexibility in the Degrees of Preferential Attachment Networks},
  pdfauthor={Thomas William Boughen; Clement Lee; Vianey Palacios Ramirez},
  pdfkeywords={networks, extremes},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title[Tail Flexibility in the Degrees of Preferential Attachment
Networks]{Tail Flexibility in the Degrees of Preferential Attachment
Networks}

% author setup
\author[1]{\fnm{Thomas William} \sur{Boughen}}\author[1]{\fnm{Clement} \sur{Lee}}\author[1]{\fnm{Vianey Palacios} \sur{Ramirez}}
% affil setup
\affil[1]{\orgdiv{School of Mathematics, Statistics and
Physics}, \orgname{Newcastle University}}

@@

\abstract{Devising the underlying generating mechanism of a real-life
network is difficult as, more often than not, only its snapshots are
available, but not its full evolution. One candidate for the generating
mechanism is preferential attachment which, in its simplest form,
results in a degree distribution that follows the power law.
Consequently, the growth of real-life networks that roughly display such
power-law behaviour is commonly modelled by preferential attachment.
However, the validity of the power law has been challenged by the
presence of alternatives with comparable performance, as well as the
recent findings that the right tail of the degree distribution is often
lighter than implied by the body, whilst still being heavy. In this
paper, we study a modified version of the model with a flexible
preference function that allows super/sub-linear behaviour whilst also
guaranteeing that the limiting degree distribution has a heavy tail. We
relate the distributions tail heaviness directly to the model
parameters, allowing direct inference of the parameters from the degree
distribution alone.}

% keywords
\keywords{networks,  extremes}

@@

The degree distribution of a network can be very informative about the
networks structure, giving some understanding about the inequality in
the influence of the nodes. Often the degree distribution is one of the
simplest places to look when trying to understand this, as the full
evolution of the network is usually not available. This makes modelling
the degree distribution an important topic in research with
contributions such as {[}ref{]}.

When looking at the degree distributions of real networks, a power law
is an attractive option to use when modelling as it is seemingly
observed in a lot of networks. Fitting the discrete power law to the
degree distribution come with the added benefit of suggesting
preferential attachment as the generating mechanism since it has been
shown to generate networks with a power law degree distribution.

If the power law is an adequate model to use for real degree
distributions has become a heated debate, with alternatives such as
\citep{Broido_2019} seeming to outperform the power law in some cases.
Additionally, {[}ref{]} find that for many real degree distributions the
body may follow a power law, the right tail does not or at least seems
to be lighter than is implied by the body whilst still being heavy. One
method for modelling the tail of the degree distributions of real
networks is to use a discretised variation of the generalised Pareto
distribution (GPD) usually dubbed the Integer GPD (GPD) where
\(X|X>v \sim \mathrm{IGPD}(\xi,\sigma,v)\) is defined by the survival:

\[
\Pr(X> x|X> v) = \left(\frac{\xi(x-v)}{\sigma} + 1\right)^{-1/\xi},\qquad x=v+1,v+2,\ldots
\] for \(v\in\mathbb Z^+, \sigma>0,\xi\in \mathbb R\).

The IGPD has been shown to be in the same domain of attraction and has
the same tail-index \(\xi\) as the regular GPD with the same parameters
by using the following quantity introduced by \citep{shimura12}:

\[
\Omega(F,n) = \left(\log\displaystyle\frac{\bar F (n+1)}{\bar F (n+2)}\right)^{-1} - \left(\log\displaystyle\frac{\bar F (n)}{\bar F (n+1)}\right)^{-1},
\] the limit of this quantity if it exists and is non-zero is exactly
the tail-index of the distribution \(F\), and if the limit is zero then
the distribution is in the Gumbel maximum domain of attraction. These
results will be useful later on when trying to establish the tail
behaviour of a network's limiting degree distribution.

These models that seem to outperform the power law do not however come
with the added benefit of suggesting a generating mechanism for the
networks in the same way the power law does. Efforts to make the
preferential attachment model more flexible have not yet remedied this
issue with \citep{krapivsky01} finding that using a sub/super-linear
preference function yields a Weibull tail and a degenerate network,
where one vertex eventually gains all new edges, respectively.

\citep{rudas07} introduces theoretical results for a PA model with a
general preference function in the cases that the network being
generated is a tree; presenting an opportunity to design a preference
function that will capture the behaviours observed in the degree
distributions of real networks. This paper studies a flexible class of
preference functions that allow for a power law body and a tail that is
heavy and flexible, and proposes a strategy for fitting this model to
real data. With good fits, this method does not only allow the tail
heaviness to be quantified, but it also allows for some inference on the
preference function assuming a general preferential attachment model is
the underlying generating mechanism.

\section{General Preferential Attachment}\label{sec-gpa}

The focus of this section is the limiting degree distribution of a
preferential attachment network with preference function \(b(\cdot)\)
where each vertex brings with it \(m\) edges. This preference function
is subject to the following conditions:

\[
b:\mathbb N \mapsto \mathbb R^+\setminus\{0\},
\]

\begin{equation}\phantomsection\label{eq-condb2}{
\sum_{k=0}^\infty\frac{1}{b(k)} = \infty.
}\end{equation}

Given these two conditions an expression for the survival of the
limiting degree distribution can be found in the case that \(m=1\);
obtained by considering a branching process that is equivalent to the
growth of the network, as in \citep{rudas07}. Theorem 1 from
\citep{rudas07} states that for the tree \(\Upsilon(t)\) at time \(t\):

\[
\lim_{t\rightarrow\infty}\frac{1}{|\Upsilon(t)|}\sum_{x\in\Upsilon(t)}\varphi(\Upsilon(t)_{\downarrow x}) = \lambda^* \int_0^\infty e^{-\lambda^* t}\mathbb E\left[\varphi(\Upsilon(t))\right]dt
\] where \(\lambda^*\) satisfies \(\hat\rho(\lambda^*)=1\).

The limiting survival can be viewed as the limit of the empirical
proportion of vertices with degree over a threshold \(k\), that is:

\[
\bar F(k) = \lim_{t\rightarrow\infty}\frac{\sum_{x\in\Upsilon(t)}\mathbb I\left\{\text{deg}(x,\Upsilon(t)_{\downarrow x})>k\right\}}{\sum_{x\in\Upsilon(t)} 1}
\] which by the previously stated theorem can also be written as:

\[
\bar F(k) = \frac{\int_0^\infty e^{-\lambda^* t}\mathbb E\left[\mathbb I\left\{\text{deg}(x,\Upsilon(t))>k\right\}\right]dt}{\int_0^\infty e^{-\lambda^* t}dt} = \prod_{i=0}^k\frac{b(i)}{\lambda^* + b(i)}
\] Additionally, using the fact that \(f(k) = \bar F(k-1) - \bar F(k)\)
the probability mass function (p.m.f.) can be shown to be:

\[
f(k) = \frac{\lambda^*}{\lambda^* + b(k)}\prod_{i=0}^{k-1}\frac{b(i)}{\lambda^*+b(i)},\qquad k\in\mathbb N.
\]

which aligns with the result from \citep{rudas07}, where the expression
is derived using the same branching process results.

Using results from \citep{shimura12} the domain of attraction of this
limiting degree distribution can be found.

\begin{proposition}[]\protect\hypertarget{prp-omega}{}\label{prp-omega}

If \(b(k) \rightarrow \infty\) as \(k\rightarrow \infty\) then \[
\bar F(k) = \prod_{i=0}^k\frac{b(i)}{\lambda^* + b(i)}
\] and

\[
\lim_{k\rightarrow\infty}\Omega(F,n) = \lim_{k\rightarrow\infty}\frac{b(k+1)-b(k)}{\lambda^*}.
\]

\end{proposition}

Proposition~\ref{prp-omega} implies that the only way to obtain a heavy
tailed degree distribution using a non-decreasing preference function is
to have that preference function be asymptotically linear. The next
subsection focuses on a particular class of these preference functions
that provide flexible behaviour but guarantee a heavy tail.

\subsection{Preferential Attachment with flexible heavy
tail}\label{sec-model}

Previously, in \citep{krapivsky01}, a preference function of the form
\(k^\alpha +\varepsilon\) has been considered. However, it has been
noted that super-linear preferential attachment (\(\alpha > 1\)) leads
to a degenerate limiting degree distribution where at some point one
vertex gains the connection from every vertex that joins the network,
additionally sub-linear preferential attachment (\(\alpha <1\)) has been
shown to lead to a light tailed limiting degree distribution. Consider a
preference function of the form:

\[
b(k) = \begin{cases}
k^\alpha + \varepsilon,&k<k_0\\
k_0^\alpha + \varepsilon + \beta(k-k_0), &k\ge k_0
\end{cases}
\] for \(\alpha,\beta, \varepsilon>0\) and \(k_0\in\mathbb N\).

Using a preference function with guaranteed linear behaviour in the
limit, allows for the inclusion of sub/super linear behaviour without
losing the heavy tails or ending up with a degenerate degree
distribution.

The limiting degree distribution resulting from using a preference
function of this form can be found to have survival:

\begin{equation}\phantomsection\label{eq-polysurv}{
\bar F(k) = \begin{cases}
\prod_{i=0}^{k}\frac{i^\alpha + \varepsilon}{\lambda^*+i^\alpha + \varepsilon},&k<k_0\\
\left(\prod_{i=0}^{k_0-1}\frac{i^\alpha + \varepsilon}{\lambda^*+i^\alpha + \varepsilon}\right)\frac{\Gamma(\lambda^*+k_0^\alpha + \varepsilon)/\beta)}{\Gamma\left((k_0^\alpha + \varepsilon)/\beta\right)} \frac{\Gamma\left(k-k_0 + 1 +\frac{k_0^\alpha + \varepsilon}{\beta}\right)}{\Gamma\left(k-k_0 + 1 +\frac{\lambda^* +k_0^\alpha + \varepsilon}{\beta}\right)},&k\ge k_0.
\end{cases}
}\end{equation}

with \(\lambda^*\) satisfying \(\hat \rho(\lambda^*)=1\) where:

\[
\hat\rho(\lambda) = \sum_{n=0}^{k_0}\prod_{i=0}^{n-1}\frac{i^\alpha + \varepsilon}{\lambda+i^\alpha + \varepsilon} + \left(\frac{k_0^\alpha + \varepsilon}{\lambda-\beta}\right)\prod_{i=0}^{k_0-1}\frac{i^\alpha + \varepsilon}{\lambda + i^\alpha + \varepsilon} 
\]

which must be solved numerically for most parameter choices. Also, note
that \(\lambda>\beta\) since when \(\lambda\le \beta\) the infinite sum
no longer converges and instead goes to infinity.

Some examples of what the degree distribution looks like are shown below
in Figure~\ref{fig-polylinsurv}:

@@

\includegraphics[width=0.8\textwidth,height=\textheight]{paper_files/figure-pdf/fig-polylinsurv-1.pdf}

@@

\caption{\label{fig-polylinsurv}Theoretical survival distributions of
the limiting degree distributions, according to various combinations of
\((\alpha, \beta, \varepsilon)\) and \(k_0=20\) of the proposed
preferential attachment model.}

@@

The survival (Equation~\ref{eq-polysurv}) can be connected to the IGPD
mentioned in Section~\ref{sec-intro} by using Sterling's approximation
of the gamma function to obtain:

\[
\bar F(k) 
\begin{cases}
=\prod_{i=0}^{k}\frac{i^\alpha + \varepsilon}{\lambda^*+i^\alpha + \varepsilon},&k<k_0,\\
\approx \left(\prod_{i=0}^{k_0-1}\frac{i^\alpha + \varepsilon}{\lambda^*+i^\alpha + \varepsilon}\right) \left(\frac{\beta(k+1-k_0)}{k_0^{\alpha}+\varepsilon} + 1\right)^{-\lambda^*/\beta},&k\ge k_0,
\end{cases}
\] meaning that for \(k\ge k_0\) the limiting degree distribution is
similar to
\(\text{IGPD}\left(\frac{\beta}{\lambda^*}, \frac{k_0^\alpha + \varepsilon}{\lambda^*},k_0-1\right)\).

To assess how close of an approximation this is the theoretical
conditional survivals are shown in Figure~\ref{fig-approx_surv} in
colour and their IGPD approximations are shown in grey. The
approximation seems to hold up fairly well even for large degrees.

@@

\includegraphics[width=0.8\textwidth,height=\textheight]{paper_files/figure-pdf/fig-approx_surv-1.pdf}

@@

\caption{\label{fig-approx_surv}Theoretical conditional survivals (grey)
alongside their IGPD approximations (coloured).}

Since \(\beta>0\), the shape parameter of the IGPD is positive and thus
the distribution is heavy tailed. Additionally the value of the shape
parameter \(\xi\) is shown in Figure~\ref{fig-polyheat} for various
parameter choices:

\includegraphics[width=0.8\textwidth,height=\textheight]{paper_files/figure-pdf/fig-polyheat-1.pdf}

\caption{\label{fig-polyheat}Heat maps of \(\xi\) for various
combinations of the parameters of the proposed model.}

The darker regions on the heat maps correspond to a heavier tail and the
lighter to a lighter tail, the red dashed line shows combinations of
\(\alpha\) and \(\beta\) that produce a limiting degree distribution
with the same tail heaviness as the Barabási-Albert model, \(\xi=0.5\).

\subsubsection{Piecewise Linear Model}\label{piecewise-linear-model}

When \(\alpha = 1\) the preference function simplifies to a piecewise
linear function with \(\beta\) representing the ratio of the gradients
of the two components:

\[
b(k) = \min(k,k_0) + \varepsilon + \mathbb I\{k\ge k_0\}\beta(k-k_0)
\] for some \(\beta, \varepsilon, k_0>0\).

Following Equation~\ref{eq-polysurv} the limiting degree distribution
is:

\begin{equation}\phantomsection\label{eq-linsurv}{
\bar F(k) = \begin{cases}
\frac{\Gamma(\lambda^*+\varepsilon)\Gamma(k+1+\varepsilon)}{\Gamma(\varepsilon)\Gamma(k+1+\lambda^*+\epsilon)},&k<k_0\\
\frac{\Gamma(\lambda^*+\varepsilon)\Gamma(k_0+\varepsilon)}{\Gamma(\varepsilon)\Gamma(k_0+\lambda^*+\varepsilon)}\times \frac{\Gamma\left(\frac{k_0+\varepsilon+\lambda^*}{\beta}\right)}{\Gamma\left(\frac{k_0+\varepsilon}{\beta}\right)}\times\frac{\Gamma\left(k-k_0 + \frac{k_0+\varepsilon}{\beta}+1\right)}{\Gamma\left(k-k_0 + \frac{k_0+\varepsilon+\lambda^*}{\beta}+1\right)},&k\ge k_0
\end{cases}
}\end{equation}

Just like the previous model, the survival can be approximated by:

\[
\bar F(k) \approx \begin{cases}
\frac{\Gamma(\lambda^*+\varepsilon)}{\Gamma(\varepsilon)} (1+\varepsilon)^{\lambda^*}\left(\frac{k}{1+\varepsilon} + 1\right)^{-\lambda^*},&k<k_0\\
\frac{\Gamma(\lambda^*+\varepsilon)\Gamma(k_0+\varepsilon)}{\Gamma(\varepsilon)\Gamma(k_0+\lambda^*+\varepsilon)}\times\left(\frac{\beta(k+1-k_0)}{k_0+\varepsilon} + 1\right)^{-\lambda^*/\beta},&k\ge k_0
\end{cases}
\]

Some examples of the possible degree distributions are shown in the
central row of Figure~\ref{fig-polylinsurv}.

\section{Recovery}\label{recovery}

The goal of was to provide a possible preference function that is able
to explain the growth of real networks with varied tail behaviour in
their degree distributions. This section aims to show that the
parameters of the model in Section~\ref{sec-model} can be recovered from
the degree distribution of a network simulated from it.

The procedure for recovering the parameters begins with simulating a
network from the model with \(N=100,000\) vertices and \(m=1\) given
some set of parameters
\(\pmb\theta = (\alpha, \beta, \varepsilon, k_0)\), obtaining the degree
counts in the form of a vector of degrees \(\pmb x = (1,2,\ldots,M)\)
and the number of vertices with those degrees \(\pmb n\) where \(M\) is
the maximum degree.

Using these and the p.m.f derived in \citep{rudas07}, the likelihood
given that \(x_i \ge l\) for all \(i =1,2,\ldots,M\) is:

\begin{align*}
L(\pmb x,\pmb n | \pmb \theta) = \left(\frac{\lambda^*}{\lambda^*+\varepsilon}\right)^{n_0}\left(\prod_{j=l}^{k_0-1}\frac{j^\alpha +\varepsilon}{\lambda^* + j^\alpha +\varepsilon}\right)^{\left(\sum_{x_i\ge k_0}n_{x_i}\right)} \prod_{l \le x_i<k_0}\left(\frac{\lambda^*}{\lambda^* +x_i^\alpha + \varepsilon } \prod_{j=l}^{k_0-1}\frac{j^\alpha + \varepsilon}{\lambda^* + j^\alpha + \varepsilon}\right)^{n_i}\\ \times \prod_{x_i\ge k_0}\left(\frac{\text{B}(x_i-k_0 + (k_0^\alpha + \varepsilon)/\beta,1+\lambda^*/\beta)}{\text{B}((k_0^\alpha + \varepsilon)/\beta,\lambda^*/\beta)}\right)^{n_i}
\end{align*}

where \(B(y,z)\) is the the beta function.

This likelihood allows inference to be made about the parameters using a
Bayesian approach using the priors:

\begin{align*}
\alpha&\sim \text{Ga}(1,0.01),\\
\beta &\sim  \text{Ga}(1,0.01),\\
k_0 &\sim \text{U}(1,10,000),\\
\varepsilon &\sim \text{Ga(1,0.01)},
\end{align*}

to obtain a posterior distribution that can then be used in an adaptive
Metropolis-Hastings Markov chain Monte Carlo (MCMC) algorithm to obtain
posterior samples. The results of this inference are shown in
Figure~\ref{fig-rec1} and Figure~\ref{fig-rec2}. For these simulated
networks \(l=2\).

\includegraphics[width=0.8\textwidth,height=\textheight]{paper_files/figure-pdf/fig-rec1-1.pdf}

\caption{\label{fig-rec1}Posterior estimates of survival function for
data simulated from the proposed model with various combinations of
(\(\alpha\),\(\beta\),\(\varepsilon\)) and \(k_0=20\).}

\includegraphics[width=0.8\textwidth,height=\textheight]{paper_files/figure-pdf/fig-rec2-1.pdf}

\caption{\label{fig-rec2}Posterior estimates of paramters for data
simulated from the proposed model with various combinations of
(\(\alpha\),\(\beta\),\(\varepsilon\)) and \(k_0=20\).}

\section{Application to Real Data}\label{application-to-real-data}

Turning now to real data, the goal is to fit the model to the degree
distributions of real networks from various sources. {[}describe
networks being used{]}.

\includegraphics[width=0.8\textwidth,height=\textheight]{paper_files/figure-pdf/fig-real1-1.pdf}

\caption{\label{fig-real1}Posterior estimates (solid red) of survival
for several real data sets and their 95\% credible intervals (dotted
red)}

Figure~\ref{fig-real1} displays the posterior estimates of the
conditional survival \(F(k|k\ge2)\) for several data sets, for many of
the data sets the fit is quite good whilst for other the fit is very
bad. This may indicate that the data sets without a good fit are
unlikely to have come from a preferential attachment model. However for
those with a good fit, it is possible to obtain information about the
underlying PA mechanism assuming that the corresponding networks did
indeed grow in that fashion.

\section{Conclusion and Discussion}\label{conclusion-and-discussion}

\section{Additional Results}\label{additional-results}

\subsection{Tail heaviness of general preferential attachment
model}\label{tail-heaviness-of-general-preferential-attachment-model}

Recall the limiting survival function:

\[
\bar F(k) = \prod_{i=0}^k \frac{b(i)}{\lambda^*+b(i)},
\]

The aim is to determine how this distribution behaves for different
choices of \(b\), specifically what maximum domain of attraction does
this distribution belong to and is it affected by the choice of
preference function \(b\). \citet{shimura12} introduces a quantity that
will help in determining what domain of attraction a discrete
distribution belongs to, that is:

For a distribution \(F\) with survival function \(\bar F\) and some
\(n\in\mathbb Z^+\) let:

\[
\Omega(F,n) = \left(\log\displaystyle\frac{\bar F (n+1)}{\bar F (n+2)}\right)^{-1} - \left(\log\displaystyle\frac{\bar F (n)}{\bar F (n+1)}\right)^{-1}
\]

\citep{shimura12} then states that if
\(\lim_{n\rightarrow\infty} \Omega(F,n) = 1/\alpha\) (\(\alpha>0\)),
then \(F\) is heavy tailed with \(\bar F(n) \sim n^{-\alpha}\).
Additionally, if \(\lim_{n\rightarrow\infty} \Omega(F,n) = 0\) then the
distribution is light tailed.

Consider a preference function \(b(\cdot)\) that fulfills:

\begin{equation}\phantomsection\label{eq-condb1}{
\lim_{n\rightarrow \infty} b(n) = \infty
}\end{equation}

Substituting in the form of \(\bar F(n)\) from \textbf{?@eq-surv} and
taking the limit, subject to Equation~\ref{eq-condb1}:

\begin{equation}\phantomsection\label{eq-omegares}{
\lim_{n\rightarrow\infty}\Omega(F,n) = \lim_{n\rightarrow\infty}\frac{b(n+2)-b(n+1)}{\lambda^*}.
}\end{equation} (see appendix for full proof).

Whilst there are many classes of functions that satisfy
Equation~\ref{eq-condb1} and Equation~\ref{eq-condb2}, the vast majority
of these result in \(\Omega(F,n) \rightarrow 0\), meaning that the
limiting degree distribution is light tailed. In fact, in order for the
limiting degree distribution to be heavy tailed, \(b\) must be
asymptotically linear (\(b(k)\sim k\)).

\section{Proofs}\label{proofs}

\subsection{Tail heaviness of GPA}\label{tail-heaviness-of-gpa}

Taking the form of the GPA degree survival: \[
\bar F(n) = \prod_{i=0}^n\frac{b(i)}{\lambda+b(i)}
\] and substituting into the formula for \(\Omega(F,n)\):

\begin{align*}
\Omega(F,n)&=\left(\log\frac{\prod_{i=0}^{n+1}\frac{b(i)}{\lambda+b(i)}}{\prod_{i=0}^{n+2}\frac{b(i)}{\lambda+b(i)}}\right)^{-1}-\left(\log\frac{\prod_{i=0}^{n}\frac{b(i)}{\lambda+b(i)}}{\prod_{i=0}^{n+1}\frac{b(i)}{\lambda+b(i)}}\right)^{-1}\\
&=\left(\log\frac{\lambda+b(n+2)}{b(n+2)}\right)^{-1}-\left(\log\frac{\lambda+b(n+1)}{b(n+1)}\right)^{-1}\\
&=\left(\log\left[1+\frac{\lambda}{b(n+2)}\right]\right)^{-1}-\left(\log\left[1+\frac{\lambda}{b(n+1)}\right]\right)^{-1}
\end{align*}

Clearly if \(b(n)=c\) or \(\lim_{n\rightarrow\infty}b(n)=c\) for some
\(c>0\) then \(\Omega(F,n)=0\). Now consider a non-constant \(b(n)\) and
re-write \(\Omega(F,n)\) as:

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  sn-nature,
]{sn-jnl}

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\raggedbottom
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Quarto Template for Springer Nature},
  pdfauthor={Author One; Author Two; Author Three},
  pdfkeywords={template, demo},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title[Quarto Template for Springer Nature]{Quarto Template for Springer
Nature}

% author setup
\author[1,2]{\fnm{Author} \sur{One}}\equalcont{These authors contributed equally to this work.}\author*[3]{\fnm{Author} \sur{Two}}\email{corresponding@email.com}\equalcont{These authors contributed equally to this work.}\author[1]{\fnm{Author} \sur{Three}}
% affil setup
\affil[1]{\orgdiv{Department of Government}, \orgname{Harvard
University}, \orgaddress{\street{1737 Cambridge
Street}, \city{Cambridge}, \postcode{2138}}}
\affil[2]{\orgdiv{Department of Statistics}, \orgname{Harvard
University}, \orgaddress{\street{1 Oxford
Street}, \city{Cambridge}, \postcode{2138}}}
\affil[3]{\orgdiv{Department of Political Science}, \orgname{Yale
University}, \orgaddress{\street{115 Prospect Street}, \city{New
Haven}, \postcode{3401}}}

@@

\abstract{The abstract serves both as a general introduction to the
topic and as a brief, non-technical summary of the main results and
their implications. Authors are advised to check the author instructions
for the journal they are submitting to for word limits and if structural
elements like subheadings, citations, or equations are permitted.}

% keywords
\keywords{template,  demo}

@@

The Introduction section, of referenced text \citep{greenwade93} expands
on the background of the work (some overlap with the Abstract is
acceptable). The introduction should not include subheadings.

Springer Nature does not impose a strict layout as standard however
authors are advised to check the individual requirements for the journal
they are planning to submit to as there may be journal-level
preferences. When preparing your text please also be aware that some
stylistic choices are not supported in full text XML (publication
version), including coloured font. These will not be replicated in the
typeset article if it is accepted.

\section{Using this template}\label{sec-template}

This Quarto template is unofficial and built out of Springer Nature's
template. Some examples of commonly used commands and features are
listed below, to help you get started.

As seen below, you can mix markdown and Latex with each other, though
it's likely best to mostly use markdown.

\subsection{Cross Referencing}\label{cross-referencing}

To reference a figure with example label ``plot'', use
\texttt{@fig-plot}. Analogously, to reference a table with example label
``data'', use \texttt{@tbl-data}. To reference a section, such as the
Introduction (Section~\ref{sec-intro}), use \texttt{@sec-intro}.

For complete information on cross referencing with Quarto, see
\url{https://quarto.org/docs/authoring/cross-references.html}.

\subsection{Citations}\label{citations}

Quarto formats citations and references automatically using the
bibliography records in your .bib file. For a citation in parentheses
use \citep{greenwade93}. Multiple citations can be given as
\citep{greenwade93, knuth1984texbook}. If the tex output is to be
included in a submission to a preprint server or publisher, the default
citation method, \texttt{citeproc}, may not always produce
bibliographies compatible with the provided \texttt{bst} styles. In this
case, you can set \texttt{cite-method:\ natbib}. See
\url{https://quarto.org/docs/authoring/footnotes-and-citations.html\#sec-biblatex}.
In this case, you may either restrict usage to the default bracketed key
citation formats supported by pandoc, such as \citep{greenwade93} or
\citep{greenwade93, knuth1984texbook}. Or, use a CSL file, several of
which are vendored in
\href{https://github.com/christopherkenny/nature/tree/main/_extensions/nature/csl}{\_extensions/nature/csl}.
The advantage of the latter is that references will be consistent across
html, docx, and pdf outputs. See
\url{https://pandoc.org/MANUAL.html\#citation-syntax} for additional
details on pandoc citation styles.

\section{Tables and Figures}\label{tables-and-figures}

To include figures, you can use Quarto syntax.

@@

\includegraphics{fig.eps}

@@

\caption{\label{fig-plot}An example figure (an empty plot)}

@@

For both figures and tables, you can use LaTeX syntax if you need
additional customizability.

For example, to use footnotes within a table, you may want to use LaTeX.

\begin{table}

\caption{\label{tbl-data}LaTeX caption text}

@@

[h]
%
\begin{tabular}{@{}llll@{}}
\toprule
Column 1 & Column 2  & Column 3 & Column 4\\
\midrule
row 1    & data 1   & data 2  & data 3  \\
row 2    & data 4   & data 5\footnotemark[1]  & data 6  \\
row 3    & data 7   & data 8  & data 9\footnotemark[2]  \\
\botrule
\end{tabular}
\footnotetext{Source: This is an example of table footnote. This is an example of table footnote.}
\footnotetext[1]{Example for a first table footnote. This is an example of table footnote.}
\footnotetext[2]{Example for a second table footnote. This is an example of table footnote.}

@@

\end{table}%
